---
title: "Quiz!"
output: learnr::tutorial
runtime: shiny_prerendered
---



```{r setup, include=FALSE}
library(learnr, reticulate)


```


##  1 

### Which programming language is this?


```{r, eval=FALSE}
#import <Foundation/Foundation.h>

int main (int argc, const char * argv[])
{
        NSLog (@"Hello, World!");
        return 0;
}
```


```{r q-1, echo=FALSE}
question("",
  answer("Objective-C", correct = TRUE),
  answer("Smalltalk"),
  answer("C"),
random_answer_order = TRUE
)
```





## 2 

### Which programming language is this?


```{r, eval=FALSE}
# include <iostream>

int main()
{
   std::cout << "Hello, world!\n";
}
```


```{r q-2, echo=FALSE}
question("",
  answer("C"),
  answer("C++", correct = TRUE),
  answer("C#"),
random_answer_order = TRUE
)
```

## 3

### Which programming language is this?

```{r, eval=FALSE}
\documentclass{plain}
\begin{document}
Hello, world!
\end{document}
```

```{r q-3, echo=FALSE}
question("",
  answer("LaTeX", correct = TRUE),
  answer("ConTeXt"),
  answer("TeX"),
random_answer_order = TRUE
)
```

## 4

### The SQL used by front-end application programs to request data from the DMBS is called: 

```{r q-4, echo=FALSE}
question("",
  answer("VDL"),
  answer("SDL"),
  answer("DML", correct = TRUE),
   answer("DDL"),
random_answer_order = TRUE
)
```

## 5

### A database language used for defining the whole database structure and schema is called:

```{r q-5, echo=FALSE}
question("",
  answer("VDL"),
  answer("SDL"),
  answer("DML"),
   answer("DDL", correct = TRUE),
random_answer_order = TRUE
)
```

## 6  
### Which of these packages allows users to run code from the Julia language in R?

```{r q-6, echo=FALSE}
question("",
  answer("RJuliaR"),
  answer("JuliaR"),
  answer("RJulia"),
   answer("JuliaCall", correct = TRUE),
random_answer_order = TRUE
)
```

## 7

### Predict the output of the following code:

```{r,  eval=FALSE}
class Test
{
    boolean[] array = new boolean[3];
    int count = 0;
  
    void set(boolean[] arr, int x)
    {
        arr[x] = true;
        count++;
    }
  
    void func()
    {
        if(array[0] && array[++count - 2] | array [count - 1])
            count++;
  
        System.out.println("count = " + count);
    }
  
  
    public static void main(String[] args)
    {
        Test object = new Test();
        object.set(object.array, 0);
        object.set(object.array, 1);
        object.func();
    }
}
```

```{r q-7, echo=FALSE}
question("",
  answer("2"),
  answer("3"),
  answer("4", correct = TRUE),

random_answer_order = TRUE
)
```

## 8

### Technique used to find the best choice of number of clusters 
```{r q-8, echo=FALSE}
question("",
  answer("screeplot()", correct = TRUE),
  answer("knn()"),
  answer("skewness()"),
  answer("dendogram()"),

random_answer_order = TRUE
)
```

## 9

### The least squares estimator in MLR is derived by:
```{r, q-9, echo=FALSE}

question("",
  answer("Minimizing the sum of squared errors", correct = TRUE),
  answer("Making the sum of squared errors equal to one"),
  answer("Minimizing the absolute difference of the residuals"),
  answer("Forcing the smallest distance between the actual and fitted values"),

random_answer_order = TRUE
)

```

## 10

### Which of the following is a server-side Java Script object? 

```{r, q-10, echo=FALSE}
question("",
  answer("Function"),
  answer("FileUpload"),
  answer("File" , correct = TRUE),
  answer("Date"),

random_answer_order = TRUE
)
 
```

## 11

### What is negative infinity in Java script? 


```{r, q-11, echo=FALSE}
 question("",
  answer("Any of below."),
  answer(" Number in JavaScript, derived by dividing number by a negative number. "),
  answer("Number in JavaScript, derived by dividing number by zero."),
  answer("Number in JavaScript, derived by dividing negative number by zero.", correct = TRUE),
random_answer_order = TRUE
)

```

